---
title: "Exploring BHL data for OCR text"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rbhl)
library(dplyr)
library(httr)
my_bhl_key = ""
options(bhl_key = my_bhl_key)
```

### Finding the target species

The **namesearch** function returns a list of species we might be interested in.

```{r}
pa <- bhl_namesearch('Platycercus')
pa
```

The **namegetdetail** function returns the Titles containing the chosen species info

```{r}
searchname = 'Platycercus adscitus (Latham, 1790)'
titles <- bhl_namegetdetail(name=searchname) 
titles <- select(titles,Titles.TitleID, Titles.ShortTitle, Titles.PublicationDate, Titles.Items) # pick out cols
titles
```

The Items field has some interesting things in it. Pull one out using dplyr:

```{r warning=FALSE}
sampleitem <- titles %>%
        filter(Titles.TitleID == 126732)  %>%
        select(Titles.Items)
sampleitem <- sampleitem$Titles.Items
sampleitem
```

Paydirt! Items contains a list of the pages that mention this species along with the ocr url. Let's get those out.

```{r, warning=FALSE}
sampleitempages <- sampleitem[[1]]$Pages # list of pages
sampleitempages <- sampleitempages[[1]] %>%
        select(ItemID,PageID,PageUrl,OcrUrl,PageTypes,PageNumbers)
sampleitempages
```

Make a http call to get the OCR text out. 

```{r}
url <- paste("",sampleitempages$OcrUrl,sep="")
httpresponse <- GET(url)
content(httpresponse)
```

Or rbhl has a method for this too:
```{r}
results <- bhl_getpageocrtext(sampleitempages$PageID)
results
```
